Collision rates of planetesimals near mean-motion resonances

### 2020-11-17 main.tex
Finish updating section 2

@@

\textbf{Add calculation of gas drag timescale on planetesimals here. Should be much longer than other timescales!}

@@

\subsection{Where Does the Dust End Up?}

>>>>

\textbf{We begin by providing a description of the dynamical effects responsible for shaping the orbital distribution of the planetesimals. The purpose of this is twofold: (1) to motivate the initial conditions used for the simulations described in section \ref{sec:ics} and (2) to justify the exclusion of certain physical effects from our simulations. Here, we focus solely on the physics relevant for full-sized ($\sim$100 km) planeteismals and leave a discussion of the effects on smaller bodies generated through collisions for section \ref{sec:dust}.}

@@

@@

\subsection{Where Does the Dust End Up?}\label{sec:dust}
